HCM SCD risk algorithm cost-effectiveness analysis

### 2020-11-27 HCM.SCD.CEanalysis/inst/rmarkdown/draft.Rmd
fix structural seros in markov model Dirichlet. add starting state costs.

Risk score algorithm details see [@mahony2014].

@@

 Name | Value | Parameter | Source 
------|-------|-----------|--------
| _Health_ ||||
| Manage with ICD | 0.637 QALY/year | $h_1$ | Noyes 2007 |
| Shock | ? utility losss | $h_2$ |  |
| HCM | ? QALY/year | $h_3$ |  |
| Death | 0 QALY/year | $h_4$, $h_5$ |  |
|       |      |      |     |
| _Cost_ ||||
| Manage with ICD | ? | $c_1$ |  |
| Non-fatal HCM event | £22,880 | $c_2$ | UK Stroke Assoc. |
| HCM | ? | $c_3$ |  |
| SCD | ? | $c_4$ |  |
| All-cause death | ? | $c_5$ |  |
|      |      |      |     |

: Model parameter values.

@@

-   Partition observed in data set
-   ICD given if number of risk factors \> 1, 2 or 3
-   ICD given if risk score \>6%
-   ICD given if risk score \>4%

>>>>

Sudden cardiac death (SCD) risk score algorithm details see [@mahony2014].

@@

 Name | Value$^*$ | Parameter | Source 
------|-------|-----------|--------
| _Health_ ||||
| Manage with ICD | 0.637 QALY/year | $h_1$ | Noyes 2007 |
| Shock | one-off and/or on-going? utility loss | $h_2$ |  |
| HCM without ICD | < 1 ? QALY/year | $h_3$ |  |
| Death | 0 QALY/year | $h_4$, $h_5$ |  |
|       |      |      |     |
| _Cost_ ||||
| Manage with ICD | ? | $c_1$ |  |
| Perform risk score | £20? |  |  |
| Implant ICD | £4,666? |  | EY02B Tariffs |
| Attention to ICD | £1,817? |  | EY10B Tariffs |
| Testing ICD | £467? |  | Tariffs |
| Non-fatal HCM event | £22,880 | $c_2$ | UK Stroke Assoc. |
| e.g shock? | one-off and/or on-going? | | |
| HCM without ICD | ? | $c_3$ |  |
| SCD | ? | $c_4$ |  |
| All-cause death | ? | $c_5$ |  |
|      |      |      |     |

: Model parameter values. $^*$either one-off/on state entry or recurring.

Table 2 gives the starting state populations for non-zero states.

Risk rule | State | Population
----------|-------|-----------
Observed  | HCM ICD | 559
      -    | HCM | 3113
Score > 4%| HCM ICD | 2561
      -    | HCM | 1111
Score > 6%| HCM ICD | 542
      -    | HCM | 3130
Risk factor >0| HCM ICD | 1785
      -    | HCM | 1887
Risk factor >1| HCM ICD | 481
      -    | HCM | 3191
Risk factor >2| HCM ICD | 78
      -    | HCM | 3594

@@

-   Partition observed in data set
-   ICD given if number of risk factors \> 0, 1 or 2
-   ICD given if risk score \>6%
-   ICD given if risk score \>4%
